Compare pseqs

### 2019-05-23 comparepseqs.Rmd
Subset

    if("clean" %in% names(args)) {
        unlink("rds-comparepseqs", recursive=TRUE)
        unlink("cache", recursive=TRUE)
    }
    if ("loadlast" %in% names(args) )
        load("session/comparepseqs.Rdata")
}
```

@@

@@

```{r save session}
save.image(file = paste0("session/comparepseqs.Rdata"))
```

>>>>

    if("clean" %in% names(args)) {
        unlink("rds-comparepseqs", recursive=TRUE)
        unlink("cache", recursive=TRUE)
    }
    if ("loadlast" %in% names(args) )
        load("session/comparepseqs.Rdata")

    if ("subset" %in% names(args))
        subset.run <- args$subset
}
```

@@

```{r subset runs}
if (exists(subset.run)) {
    rds <- rds[[subset.run]]
}

print(rds)
quit()
```

@@
